\documentclass[margin]{res}
\setlength{\textwidth}{5.1in}

\begin{document}

 \moveleft.5\hoffset\centerline{\large\bf William P. Woodruff}
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
 \moveleft.5\hoffset\centerline{william@tuffbizz.com}
 \moveleft.5\hoffset\centerline{woodruffw.us - github.com/woodruffw}
 \moveleft.5\hoffset\centerline{(917) 587-5721}


\begin{resume}
 

\section{EDUCATION} {\sl The Bronx High School of Science,} Bronx, NY,
                expected June 2014. \\
                Focus: Computer Science \\
                {\sl The University of Maryland,} College Park, MD,
                expected class of 2018.
 
 
\section{SKILLS} {\sl Languages:} C, Java, Perl, C++, C\#, shell, HTML/CSS/JS, NASM, and Lisp. \\
				{\sl Frameworks and Libraries:} OpenGL, ImageMagick, cURL, .NET, and X11. \\
				{\sl Software:} Inkscape, GIMP, Audacity, Reason, and Visual Studio. \\
                {\sl Operating Systems:} Linux, *BSD, Solaris, Darwin (OS X), and Windows.
 
\section{EXPERIENCE} {\sl Computer Systems Assistant} \hfill Summer 2012 \\
                M.S 54 - The Booker T. Washington Middle School,
                Manhattan, NY
                 \begin{itemize}  \itemsep -2pt
                 \item  Installed new computer hardware and computer lab equipment,
                 		including projectors and smart boards. 
                 \item	Imaged new machines with OSes, devised group policies, and transferred
                 		old student accounts, records, and files to the new systems.
                 \end{itemize}
                 
                 {\sl Computer Science Demonstrator} \hfill 2011-2014 \\
                The Bronx High School of Science, Bronx, NY
                  \begin{itemize}
                   \item Demonstrated Bronx Science's programs in Computer Science
                   		 (AP CS, Robotics, Game Programming) to prospective and admitted students.
                   \item Developed special demo programs for demonstrations, including 
                   		 examples of genetic learning in robots and graphics demonstrations.
                   \end{itemize} 
 
                {\sl Contracted Computer Services and Repair} \hfill February 2013 - Present \\
                Freelance, Manhattan, NY 
                 \begin{itemize}  \itemsep -2pt
                 \item	Assisted clients in resolving hardware and software issues
                 		across Windows, OS X, and Linux.
                 \item	Developed scripts and programs for backup, system maintenance,
                 		and emergency reporting. 
                 \end{itemize} 
                 
 
\section{COMMUNITY \\ SERVICE} Active summer volunteer at the Yorkville Common Pantry.
								Beginning in 2012, assisted in planned meal services 
								(breakfast and dinner) as well as in food availability 
								programs. Cooked and served meals to pantry members, 
								bagged groceries, and performed logistics.
								
\section{HONORS} National Latin Examination, Summa Cum Laude (2011) \\
				 National Latin Examination, Magna Cum Laude (2012, 2013) \\
				 AP Scholar Award (2013) \\
				 HackBCA Winner, Top 20 (2014) \\

\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
            Bronx Science Photography Club (2011, 2012) \\
            Bronx Science History Club (2012) \\
            Bronx Science Improv Club (2011 - 2013) \\
            Bronx Science DIY Electronics Club - Founder and President (2012-) \\
            Other interests include: Handball, Bicycling, Reading, Politics, and Philosophy.

\end{resume}
\end{document}




